---
title: "Project 3: STAT302package Tutorial"
author: "Andrey Risukhin"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{STAT302package Tutorial}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(STAT302package)
```

## Stat 302 Package

Welcome to Andrey Risukhin's Stat 302 Package! With this package, users can:

- Run t-tests for the lesser, greater, and two-sided alternate hypothesis using `my_t.test()` (note, this script is in the file labeled `my_t_test.R`)

- Fit a linear (polynomial) model to data using `my_lm()`

- Use `my_knn_cv`: a custom function to return knn predictions and evaluate its quality through cross validation.

- Use `my_rf_cv`: A custom random forest prediction function that also returns cross validation error.

### Installation

To use this package, first install it with:

```{r, eval = FALSE}
devtools::install_github("andreyrisukhin/STAT302package")
```

Then, run the following to use it in a given project:

```{r, eval = FALSE}
library(STAT302package)
```

## T Test

```{r}
# Get the data
gap_data <- STAT302package::my_gapminder#$lifeExp
life_exp_data <- my_gapminder$lifeExp
# Perform t-tests
ah_not_60 <- my_t.test(life_exp_data, "two.sided", 60)
ah_less_60 <- my_t.test(life_exp_data, "less", 60)
ah_greater_60 <- my_t.test(life_exp_data, "greater", 60)
```
The test for the alternate hypothesis being not equal to 60 returns a P-value of `r ah_not_60$p_val`.

The test for the alternate hypothesis being less than 60 returns a P-value of `r ah_less_60$p_val`.

The test for the alternate hypothesis being greater than 60 returns a P-value of `r ah_greater_60$p_val`.

Given an alpha of 0.05, we fail to reject the first and third null hypotheses, and fail to conclude that the mean life expectancy is not equal to 60 or is greater than 60. We are able to reject the second null hypothesis, concluding that the mean life expectancy is less than 60. 

## Linear Model

```{r}
# Get the data
gap_data <- STAT302package::my_gapminder#$lifeExp
# Fit with linear regression
output <- my_lm(lifeExp ~ gdpPercap + continent, data = gap_data)
output
```
Given this output, we conclude the following:

- The gdpPercap coefficient has the lowest value ("Estimate") and standard error of any coefficients. Therefore, gdpPercap is a feature which does not vary much, and in which a small change strongly affects the model prediction (hence the small coefficient). 

- The hypothesis test associated with the gdpPercap coefficient is a two-sided test, in which we reject the null hypothesis that this coefficient is zero because our P-value is much less than the threshold of 0.05. 

Let us plot the actual and fitted values:

```{r}
# To get Actual vs. Fitted, you need to multiply X %*% beta. To get beta, use your estimates. To get X, use `model.matrix(FORMULA, DATA)`
beta <- c(output[[1]], output[[2]], output[[3]], output[[4]], output[[5]], output[[6]])
X <- model.matrix(lifeExp ~ gdpPercap + continent, data = gap_data)
actual_v_fitted <- X %*% beta


```
