---
title: "Project 3: STAT302package Tutorial"
author: "Andrey Risukhin"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{STAT302package Tutorial}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(STAT302package)
```

## Stat 302 Package

Welcome to Andrey Risukhin's Stat 302 Package! With this package, users can:
- Run t-tests for the lesser, greater, and two-sided alternate hypothesis using `my_t.test()` (note, this script is in the file labeled `my_t_test.R`)
- Fit a linear (polynomial) model to data using `my_lm()`
- `my_knn_cv`: a custom function to return knn predictions and evaluate its quality through cross validation.
- `my_rf_cv`: A custom random forest prediction function that also returns cross validation error.

### Installation

To use this package, first install it with:

```{r, eval = FALSE}
devtools::install_github("andreyrisukhin/STAT302package")
```

Then, run the following to use it in a given project:

```{r, eval = FALSE}
library(STAT302package)
```

## Linear Model

## T Test
